TacticToe: Learning to Prove with Tactics

### 2018-03-23 tactictoe_jv.tex
Some more edits

\[\mathit{CurEvaluation}(a_i) =
  \sum_{a' \in \mathit{Descendant}(a_i)} \frac{\mathit{PriorEvaluation}(a')} {card\
  \mathit{Descendant}(a_i) + \mathit{Failure}(a_i)}\]

@@

\[\mathit{CurPolicy}(a_i) = \frac{1 +
\mathit{Visit}(a_i)}{\sqrt{\mathit{Visit}(p)}}\]
The policy can be seen as a skewed percentage of the number of times a node was
visited. The square root favors exploration of nodes with
few visits. The coefficient $c_{exploration}$ is experimentally determined and
adjusts the trade-off between exploitation and exploration.
\end{definition}

@@

\paragraph{Resolution}
The search ends when the algorithm reaches one of these 3 conditions:
\begin{itemize}
\item It finds a proof, i.e., the root node is solved. In this case,
the search returns a minimized and
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It saturates, i.e., there are no tactics to be applied to any open goal.
This occurs less than 0.1 percent of the time in the full-scale experiment.
And this happens only at the beginning of the \holfour library, where the
training
data
has very few tactics.
\item It exceeds a given time limit (default is set to 60 seconds).
\end{itemize}

@@

\paragraph{Prior policy}\label{sec:policy}
Similarity between goals produced by the tactic predictor are hard
to translate into a prior policy, so we rely solely on the prediction order
to estimate the probability with which each tactic should be tried.
Let $\mathfrak{T}$ be a search tree after a number of MCTS steps.
Let $p$ be a selected node in $\mathfrak{T}$ and $g$ its open goal. We order
the list of $n$ productive tactics already
applied to $g$ by their similarity score. We note the resulting list
$t_0,\ldots,t_{n-1}$.
Let $c_{policy}$ be a constant heuristic optimized during our experiments.
We calculate the prior policy of a child $a_i$ produced by the tactic
$t_i$ by:
\[PriorPolicy(a_i) = (1 - c_{policy})^{i} * c_{policy}\]

@@

\[WideningPolicy(p) = (1 - c_{policy})^{n} * c_{policy}\]

@@

We now concentrate on the definition of a reasonable evaluation function for the
output of tactics. Intuitively, a list of goals is worth exploring further if
we believe there exists a short proof for it. We could estimate the likelihood
of finding such a proof from
previous proof searches. However, extracting lists of goals from all proof
attempts creates too much data which slows down the prediction algorithm.
So, we only
collect outputs of tactics tested during orthogonalization (see
Section~\ref{sec:ortho}). We
declare a list of goals $l$ to be \textit{positive} if it has been produced
by the winner of an orthogonalization competition.
The set of positive examples in
$\mathit{Predictions}^{\mathit{goal\_list}}_k(l)$ is denoted
$\mathit{Positive}^{\mathit{goal\_list}}_k(l)$.
We chose $k=10$ as a default evaluation radius in our experiments.
And we evaluate a node $a$ through the list of goals $G(a)$ it
contains using the prior evaluation function:
\begin{align*}
\mathit{PriorEvaluation}_k (a) &=
  \frac{card\ \mathit{Positive}^{\mathit{goal\_list}}_k(G(a)}{k}\\
\end{align*}

>>>>

\[\mathit{CurEvaluation}(a_i) =
  \sum_{a' \in \mathit{Descendant}(a_i)} \frac{\mathit{PriorEvaluation}(a')}
  {|\mathit{Descendant}(a_i)| + \mathit{Failure}(a_i)}\]

@@

\[\mathit{CurPolicy}(a_i) = \frac{1 +
\mathit{Visit}(a_i)}{\sqrt{\mathit{Visit}(p)}}\]
The policy can be seen as a skewed percentage of the number of times a node was
visited. The square root favors exploration of nodes with
  few visits. The coefficient $c_{\mathit{exploration}}$ is experimentally determined and
adjusts the trade-off between exploitation and exploration.
\end{definition}

@@

\paragraph{Resolution}
The search ends when the algorithm reaches one of these 3 conditions:
\begin{itemize}
\item It finds a proof, i.e., the root node is solved. In this case,
the search returns a minimized and
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It saturates, i.e., there are no tactics to be applied to any open goal.
This occurs less than 0.1 percent of the time in the full-scale experiment.
And this happens only at the beginning of the \holfour library, where the
training
data
has very few tactics.
\item It exceeds a given time limit (60 seconds by default).
\end{itemize}

@@

\paragraph{Prior policy}\label{sec:policy}
Similarity between goals produced by the tactic predictor are hard
to translate into a prior policy, so we rely solely on the prediction order
to estimate the probability with which each tactic should be tried.
Let $\mathfrak{T}$ be a search tree after a number of MCTS steps.
Let $p$ be a selected node in $\mathfrak{T}$ and $g$ its open goal. We order
the list of $n$ productive tactics already
applied to $g$ by their similarity score. We note the resulting list
$t_0,\ldots,t_{n-1}$.
Let $c_{\mathit{policy}}$ be a constant heuristic optimized during our experiments.
We calculate the prior policy of a child $a_i$ produced by the tactic
$t_i$ by:
\[\mathit{PriorPolicy}(a_i) = (1 - c_{\mathit{policy}})^{i} * c_{\mathit{policy}}\]

@@

\[\mathit{WideningPolicy}(p) = (1 - c_{\mathit{policy}})^{n} * c_{\mathit{policy}}\]

@@

We now concentrate on the definition of a reasonable evaluation function for the
output of tactics. Intuitively, a list of goals is worth exploring further if
we believe there exists a short proof for it. We could estimate the likelihood
of finding such a proof from
previous proof searches. However, extracting lists of goals from all proof
attempts creates too much data which slows down the prediction algorithm.
So, we only
collect outputs of tactics tested during orthogonalization (see
Section~\ref{sec:ortho}). We
declare a list of goals $l$ to be \textit{positive} if it has been produced
by the winner of an orthogonalization competition.
The set of positive examples in
$\mathit{Predictions}^{\mathit{goal\_list}}_k(l)$ is denoted
$\mathit{Positive}^{\mathit{goal\_list}}_k(l)$.
We chose $k=10$ as a default evaluation radius in our experiments.
And we evaluate a node $a$ through the list of goals $G(a)$ it
contains using the prior evaluation function:
\begin{align*}
\mathit{PriorEvaluation}_k (a) &=
  \frac{|\mathit{Positive}^{\mathit{goal\_list}}_k(G(a))|}{k}\\
\end{align*}
